Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Lemmas.tex
getting closer

The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$, and is otherwise identical.  (This can be shown more formally via a coupling argument.)
Let $V_\ell$ be the conditional expectation of this second counter's value when it is stopped,
given that its current value is $\ell$ and it has not been stopped.  Observe that $V_\ell = \ell + V_0$.
Enumerating outcomes (either the counter increments or not; either it stops or it continues) provides $V_0 = f(A)\frac1{\log(s)} + f(A) (1-\frac1{\log(s)}) V_1 + (1-f(A))(1-\frac1{\log(s)}) V_0$.
Using $V_1 = 1 + V_0$ simplifies this to 
$V_0 = f(A) + (1-\frac1{\log(s)}) V_0$.
Noting $V_0$ is finite and solving for $V_0$ provides
$V_0 = f(A) \log(s)$.
Thus, the conditional expected number of pulls (given the history at time $\tau_m$) by an agent with a type in $A$ during times in $[\tau_m, \tau_{m-1})$ is no more than $f(A) \log(s)$.

>>>>

The expected value of this counter when it is stopped is bounded above by the expected stopped value of another counter whose conditional probability of being stopped is exactly $1/\log(s)$.  (This can be shown more formally via a coupling argument.)
Let $V_\ell$ be the conditional expectation of this second counter's value when it is stopped,
given that its current value is $\ell$ and it has not been stopped.  Observe that $V_\ell = \ell + V_0$.
Enumerating outcomes (either the counter increments or not; either it stops or it continues) provides $V_0 = f(A)\frac1{\log(s)} + f(A) (1-\frac1{\log(s)}) V_1 + (1-f(A))(1-\frac1{\log(s)}) V_0$.
Using $V_1 = 1 + V_0$ simplifies this to 
$V_0 = f(A) + (1-\frac1{\log(s)}) V_0$.
Noting $V_0$ is finite and solving for $V_0$ provides
$V_0 = f(A) \log(s)$.
Thus, the conditional expected number of pulls (given the history at time $\tau_m$) by an agent with a type in $A$ during times in $[\tau_m, \tau_{m-1})$ is no more than $f(A) \log(s)$.

### 2018-06-06 algorithm_regret.tex
checking over changes from david
getting closer

For most of the proof, we will focus on the case $\EarlyCut{s} \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
\dkedit{The total expected regret incurred in these phases is at most
$O(\ARMNUM \MAXR \cdot \log(T) \Diam^2 d^2 \sigma^2/\TieCutoff^2
\cdot \log (\log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2)
\leq O(\ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3)$,
by crudely bounding $\log y \leq O(\sqrt{y})$.}

@@

We next bound the regret incurred in time steps with large regret.
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > \pfedit{t_{s+1}-t_{s}}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{\dkedit{\EarlyCut{s}}}{2\Diam d}}, no agent at time $t$ will incur
regret more than \EarlyCut{s}.
\dkcomment{Instead of the extra case distinction, I had thought of
  defining \EarlyCut{s} to be the minimum of the current definition and
  \TieCutoff. Unfortunately, I think that we cannot necessarily apply
  Lemma~\ref{lem:right-choice} with that definition. Just putting that
  here in case you are thinking of simplifying the proof this way.}

@@

\begin{align*}
\sum_{s = 1}^T \sum_{t=t_s}^{t_{s+1}-1}
  \Prob{\mbox{incur regret exceeding } \EarlyCut{s} \mbox{ at step } t} \cdot \MAXR
& \leq
 \sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
\\ & \leq 12 \ARMNUM^2 d \MAXR.
\end{align*}

Adding all \dkedit{four} types of regret terms,
and substituting that 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most

\begin{align*}
\lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
\dkedit{+ \ARMNUM \MAXR \log^2(T)}
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)}
\\ & = 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
\end{align*}
\end{emptyextraproof}

>>>>

For most of the proof, we will focus on the case $\EarlyCut{s} \leq \TieCutoff$.
The remaining phases are the ones with
$s \leq \frac{128}{1.8} \cdot \log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2$.
Each such phase lasts for at most $\ARMNUM \cdot \log(s)$ steps
in expectation by Lemma~\ref{lem:phase-length},
and each step incurs regret at most \MAXR.
The total expected regret incurred in these phases is at most
$O(\ARMNUM \MAXR \cdot \log(T) \Diam^2 d^2 \sigma^2/\TieCutoff^2
\cdot \log (\log(T) \cdot \Diam^2 d^2 \sigma^2/\TieCutoff^2)
\leq O(\ARMNUM \MAXR \log^2(T) \cdot \Diam^3 d^3 \sigma^3/\TieCutoff^3)$,
by crudely bounding $\log y \leq O(\sqrt{y})$.

@@

We next bound the regret incurred in time steps with large regret.
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > \pfedit{t_{s+1}-t_{s}}$.
By Lemma~\ref{lem:right-choice},
under \AccEU{\tau_s^k}{\frac{\EarlyCut{s}}{2\Diam d}}, no agent at time $t$ will incur
regret more than \EarlyCut{s}.

@@

\begin{equation*}
\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
\leq 12 \ARMNUM^2 d \MAXR.
\end{equation*}
%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.  What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}

Adding all four types of regret terms,
and substituting that 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most

\begin{align*}
\lefteqn{O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)}
\\ & = 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right).\QED
\end{align*}
\end{emptyextraproof}
